SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-11-08 docs/questioning.tex
Analysis became Discussion - more on the discussion section.

In this section we categorize and describe the various mechanisms
developed to detect the attacks described in
Section~\ref{sec:attacks}. We accompany our descriptions with comments
related to the following dimensions: a) diagnostic performance, b)
computational performance, c) security, d) ease of use, and e)
detection locus. We treat f) availability separately in the
``Analysis" section (\ref{sec:analysis}).

@@

\section{Analysis}
\label{sec:analysis}

@@

Table~\ref{tab:comp} indicates that the authors of 3 out of 34
({\bf 8.8\%}) publications, provided complete quadruples.
On the other hand, we see that 4 out of
34 ({\bf 11.7\%}) were not tested at all
in terms of diagnostic performance. In this cases,
all the four elements of the quadruples are not
available ({\sc na}).
% Maybe we should comment on the fact that these are
% frameworks coming from the etiological category
% and detect the attacks ``by design".
An interesting observation is that 10 out of 34
({\bf 29.41\%}) of the authors performed only attacks
during their tests and did not test their mechanisms
to see if they produce any false alarms. The corresponding
quadruples in this case, are the ones that contain {\sc tp} and
{\sc fn} results but {\sc tn} and {\sc fp} results are not
available ({\sc na}). This stresses the fact that authors
of these mechanisms were more interested to make sure that
their mechanisms can detect known attacks than to see how
they respond under normal conditions.
In some occasions (where the number of {\sc tp} results
are not quantified), authors did not mention how many or
which attacks they performed.
Moreover, we observe in some cases, that even if
the authors report the existence of possible
false positive and negative results, they have not
quantified them ({\sc nq}).

@@

\section{Discussion and Lessons Learned}

Our findings indicate that currently, the testing of
the diagnostic performance of
mechanisms that detect top web application attacks
has not a standard form. In addition,
there are many mechanisms that are tested in a poor manner.

A reasonable argument would be that many
mechanisms (especially the ones coming from the
etiological category), do not need to be established
purely through testing since they provide systematic
arguments as to why their design is secure against attacks.
However, their implementations are not always efficient
and as we observed they can be circumvented.

>>>>

In this section we categorize and describe the various mechanisms
developed to detect the attacks described in
Section~\ref{sec:attacks}. We accompany our descriptions with comments
related to the following dimensions: a) diagnostic performance, b)
computational performance, c) security, d) ease of use, and e)
detection locus. We treat f) availability separately in the
``Discussion" section (\ref{sec:discussion}).

@@

\section{Discussion}
\label{sec:discussion}

@@

Table~\ref{tab:comp} indicates that the authors of 3 out of 34
({\bf 8.8\%}) publications, provided complete quadruples.
On the other hand, we see that 4 out of
34 ({\bf 11.7\%}) were not tested at all.
In this cases, all the four elements of the
quadruples are not available ({\sc na}).
% Maybe we should comment on the fact that these are
% frameworks coming from the etiological category
% and detect the attacks ``by design".
An interesting observation is that 10 out of 34
({\bf 29.41\%}) of the authors performed only attacks
during their tests and did not test their mechanisms
to see if they produce any false alarms. The corresponding
quadruples in this case, are the ones that contain {\sc tp} and
{\sc fn} results but {\sc tn} and {\sc fp} results are not
available ({\sc na}). This stresses the fact that authors
maybe more interested into making sure that
their mechanisms can detect known attacks than seeing how
they respond under normal conditions.
In some occasions (where the number of {\sc tp} results
are not quantified), authors did not mention how many or
which attacks they performed.
Also, in some cases, we observe that even if
the authors report the existence of possible
false positive and negative results, they have not
quantified them ({\sc nq}).

@@

\section{Lessons Learned}

In this section we point out our key findings and
discuss the lessons derived from our research.
We also argue that some of our observations may be
good reasons why the mechanisms are not adopted in practice.

One of our key findings indicate that currently,
the testing of the diagnostic performance of
mechanisms that detect top web application attacks
has not a standard form. In addition,
there are many mechanisms that are tested in a poor
manner. In many cases researchers tend not to
provide the false positive and negative results
that their tools may produce. Discussing
about the existence of such results and not
quantifying them may be a good reason to not use
such a mechanism.

A reasonable argument would be that many
mechanisms (especially the ones coming from the
etiological category), do not need to be established
purely through testing since they provide systematic
arguments as to why their design is secure against attacks.
However, implementations are not always efficient
and as we observed they can be circumvented.
